WSSSPE4-paper-reviewer-response

### 2018-01-05 WSSSPE4_report/WSSSPE4_paper.tex
addressing reviewer comment about conclusion section

In WSSSPE4, we heard about a number of interesting projects and ideas, and used those
ideas to create and form working groups, intended to start at the workshop and then
continue afterwards, to address challenges that arose from the workshop ideas.  This workshop
has reinforced the lesson from WSSSPE3 that it is relatively easy to get motivated people
to attend a meeting and productively spend their time there both doing work and planning
more work, but it is very hard to get that additional work after the meeting to take place.
The main problem seems to be one of time.  Once the attendees have agree to spend
their time at the workshop, they put their energy into doing so productively, but they have not
really committed themselves to anything more than this, so their energy and effort trails
off, as all of their other commitments (particularly, those they are funded to do as part of
their jobs) come back to the fore. Without a process to resolve this concern, the utility of
further multi-day WSSSPE workshops is unclear.

>>>>

In WSSSPE4, we heard about a number of interesting projects and ideas, and used those
ideas to create and form working groups, intended to start at the workshop and then
continue afterwards, to address challenges that arose from the workshop ideas. This workshop
has reinforced the lesson from WSSSPE3 that it is relatively easy to get motivated people
to attend a meeting and productively spend their time there both doing work and planning
more work, but it is very hard to get that additional work after the meeting to take place.
The main problem seems to be one of time.  Once the attendees have agree to spend
their time at the workshop, they put their energy into doing so productively, but they have not
really committed themselves to anything more than this, so their energy and effort trails
off, as all of their other commitments (particularly, those they are funded to do as part of
their jobs) come back to the fore. Without a process to resolve this concern, the utility of
further multi-day WSSSPE workshops is unclear, at least to start new activities.  On a more
positive note, WSSSPE4 was successful as a gathering place to discuss scientific
software sustainability, and for groups that are already in place or that can be composed
of related funded activities to meet.  Future WSSSPE meetings will likely combine these
functions: a meeting place for like-minded individuals, a place to share experiences and
lessons learned, and a place for both existing groups and sets of related projects to meet
in person.  Other parts of the WSSSPE infrastructure (the email list and the Slack) will
be used both for general discussions, as well as for groups that choose to focus
on specific problems.

After WSSSPE4, we also have learned enough to summarize the areas of active work
in sustainable scientific software, based on the WSSSPE4 mission and vision statements, the WSSSPE4 call for participation (based on topics in previous WSSSPE meetings), and the working groups formed in WSSSPE4.  Following the example of the recently funded US project,
``Conceptualizing a US Research Software Sustainability Institute (URSSI)\footnote{\url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1743188}},'' the high-level
version of these areas is: functioning of 1) the individual and team, 2) the research software, and 3) the research field itself, with six specific topics, as shown in Table~\ref{tab:topics}

\begin{table}[h]
\centering
\caption{Scientific Software Sustainability Research Topics and Areas}
\label{tab:topics}
\begin{tabular}{|l|c|c|c|}
 \hline
Topics \textbackslash\ Areas & Individual and team &  Research software & Research field  \\
 \hline
Principles and Best Practices & \checkmark & \checkmark & \checkmark  \\
 \hline
Careers & \checkmark &  &   \\
 \hline
Learning & \checkmark &  &   \\
 \hline
Credit & \checkmark &  & \checkmark  \\
 \hline
Organization and community & \checkmark &  &  \checkmark \\
 \hline
Common Infrastructure &  & \checkmark &   \\
 \hline
\end{tabular}
\end{table}

### 2018-01-05 WSSSPE4_report/jors-response.tex
addressing reviewer comment about conclusion section

\title{WSSSPE4-paper-reviewer-response}
\author{Daniel S. Katz}
\date{December 2017}

@@

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to 1 title page, \textcolor{red}{9.5} pages of body, and 3 pages of references, a reduction of \textcolor{red}{5.5} of the original 18 pages.

\textcolor{red}{Can we remove 1.5 more pages?}

@@

\textcolor{red}{This paragraph is the main thing that has not been addressed yet. (Note that what the reviewer calls 4 and 5 are now 5 and 6.)}

>>>>

\title{WSSSPE4-paper-reviewer-response}
\author{Daniel S. Katz}
\date{January 2018}

@@

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to 1 title page, \textcolor{red}{10} pages of body, and 3 pages of references, a reduction of \textcolor{red}{4} of the original 18 pages.

\textcolor{red}{Can we remove more pages? Sandra is working on Section 6.}

@@

We particularly thank the reviewer for this point.  We realized that this was a weakness, but were unsure how to address it.  We've now followed this useful suggestion, and added to the
conclusions paragraph.
